FEM Model Analysis

### 2020-11-26 FEM_R/model_analysis.Rmd
Changed name of analysis document
Big refactor to rename ugly and inconsistent "cross-validation/crossvalidation/cross_validation" file names for crossval. Now replaced with "CV" everywhere

---
title: "R Notebook"
output: html_notebook
---

@@

```{r include=FALSE}
# names for T-tests directory and filename stem
CV1 <- "ELSA_CrossValidation1/T-tests/"
stem <- "CV1_all_waves_"
# Read in files
cv_uw <- read.csv(paste0(CV1, stem, "unweighted.csv"))
cv_demog <- read.csv(paste0(CV1, stem, "demog.csv"))
cv_binhlth <- read.csv(paste0(CV1, stem, "binhlth.csv"))
cv_binecon <- read.csv(paste0(CV1, stem, "binecon.csv"))
cv_risk <- read.csv(paste0(CV1, stem, "risk.csv"))
# Now collect into list and rename vars and cols for clarity
cv_list <- list(cv_uw, cv_demog, cv_binhlth, cv_binecon, cv_risk)
cv_list <- lapply(cv_list, rename_first_var, prefix='CV')
cv_list <- lapply(cv_list, shorten_columns)
cv_list <- lapply(cv_list, function(x) { x[is.na(x)] <- 0; x} )
```

@@

# Load in whole stock pop, plus the CV2 summary output file
long <- read_dta('../input_data/ELSA_long.dta')
CV2 <- read_dta('ELSA_CrossValidation2/ELSA_CrossValidation2_summary.dta')

>>>>

---
title: "FEM Model Analysis"
output: html_notebook
---

@@

```{r include=FALSE}
# names for T-tests directory and filename stem
CV1 <- "ELSA_CV1/T-tests/"
stem <- "CV1_all_waves_"
# Read in files
cv_uw <- read.csv(paste0(CV1, stem, "unweighted.csv"))
cv_demog <- read.csv(paste0(CV1, stem, "demog.csv"))
cv_binhlth <- read.csv(paste0(CV1, stem, "binhlth.csv"))
cv_binecon <- read.csv(paste0(CV1, stem, "binecon.csv"))
cv_risk <- read.csv(paste0(CV1, stem, "risk.csv"))
# Now collect into list and rename vars and cols for clarity
cv_list <- list(cv_uw, cv_demog, cv_binhlth, cv_binecon, cv_risk)
cv_list <- lapply(cv_list, rename_first_var, prefix='CV')
cv_list <- lapply(cv_list, shorten_columns)
cv_list <- lapply(cv_list, function(x) { x[is.na(x)] <- 0; x} )
```

@@

# Load in whole stock pop, plus the CV2 summary output file
long <- read_dta('../input_data/ELSA_long.dta')
CV2 <- read_dta('ELSA_CV2/ELSA_CV2_summary.dta')
